Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-05-29 ms.tex
started eliminating material that will go in the supplement. Also added postage stamps for the final reference star collection.

For the photometric reduction, I used the \texttt{ccdproc} package to generate master flat field and bias files.
I combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.

As an initial start, I created a time series for the night of UT 2016-06-12.
I used aperture photometry with a source radius of 4 pixels, an inner aperture annulus of 5 pixels and an outer aperture radius of 8 pixels for the background.
I choose 6 reference stars of similar brightness and which were nearby the source on the CCD.
I use the \texttt{photutils} python package for the aperture photometry.
The resulting raw time series can be seen in \ref{fig:initTseries}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{initial_t_series.pdf}
\caption{Quick raw time series for UT 2016-06-12. No aperture centering was done (there were fixed apertures with time).
No bias or flat field corrections were applied.}\label{fig:initTseries}
\end{centering}
\end{figure}

The initial time series has huge fluctuations (and even goes negative! due to poor aperture centering at the start).
I used \texttt{photutils.centroid\_2g} to do 2D Gaussian centroiding to choose the aperture positions to start with.
The guess position and \texttt{centroid\_2g} position for the target \sha\ are shown in Figure \ref{fig:centroid2g}.
Adding a centroiding routine significantly improves the precision as seen in Figure \ref{fig:secTseries}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{centering.pdf}
\caption{The guess position of (750.7,682.4) is shown as a cyan circle. The \texttt{centroid\_2g} position of (749.7,681.1) is shown as a red circle.}\label{fig:centroid2g}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{second_t_series.pdf}
\caption{Same data for UT 2016-06-12 as Figure \ref{fig:initTseries}.
This time aperture centroiding was done.
No bias or flat field corrections were applied.}\label{fig:secTseries}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{second_t_series_bias_flat.pdf}
\caption{Same data for UT 2016-06-12 as Figure \ref{fig:initTseries}.
This time bias correction, flat field correction and aperture centroiding was done.
Note that the target, reference stars 2 and 3 have smaller deviations at 0.81 days.}\label{fig:secTseriesBiasFlat}
\end{centering}
\end{figure}

It turns out that the large flux excursions in Figure \ref{fig:secTseries} and \ref{fig:secTseriesBiasFlat} are due to some bumps pointing errors and so substantial fractions of flux fall outside the source apertures.
I solved this problem by increasing the size of the subarray box (from 10 pix width to 18 px) so that the source would be found even if it wanders.
This results in much smaller flux excursions, as seen in Figure \ref{fig:secTseriesWiderBox}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{second_t_series_wider_box.pdf}
\caption{Same data for UT 2016-06-12 as Figure \ref{fig:initTseries}.
Bias correction, flat field correction and aperture centroiding was done.
The aperture centering (2D Gaussian fits) was performed with a wider 18 pixel box to allow for pointing wander.}\label{fig:secTseriesWiderBox}
\end{centering}
\end{figure}

We considered several ways to do reference summation.
Under consideration were two choices:
\begin{itemize}
	\item How to weight the stars (by flux, equally, variance)?
	\item Which stars to include in the summation?
\end{itemize}
Figure \ref{fig:refSumMethods} shows these 4 combinations of these two choices.
Clearly reference star 2 adds noise to the time series, but this does not affect the total summation method since it has lower flux.
When normalizing each time series before summation, this appears to decrease the linear trend in the data.
In all cases, there is an apparent transit-like feature near JD = 2457551.82.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/reference_method.pdf}
\caption{Corrected time series for \shStar\ when using different combinations of averaging the reference stars: i) Summing all stars equally ii) Summing the best stars [1,3,4,5,6], iii) Summing the normalized time series of the best stars iv) summing the normalized time series of the best stars.}\label{fig:refSumMethods}
\end{centering}
\end{figure}

Figure \ref{fig:starLabels} shows the reference stars used in the initial analysis.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/st_labels.pdf}
\caption{\shStar\ at the center and the reference stars used for the photometry.}\label{fig:starLabels}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/postage_stamps.pdf}
\caption{Postage stamps of apertures used for each source (before centroiding).}\label{fig:starPostageGuess}
\end{centering}
\end{figure}

Source centroiding was performed with \texttt{centroid\_2g} within \texttt{photutils} to do 2-D Gaussian fitting. Figure \ref{fig:starPostageCen}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/postage_stamps_centered.pdf}
\caption{Postage stamps of apertures used for each source, after centroiding with \texttt{centroid\_2g} with the initial guesses shown in Figure \ref{fig:starPostageGuess}.}\label{fig:starPostageCen}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/postage_stamps_r09px_cen.pdf}
\caption{Postage stamps of apertures used for each source, after centroiding and using a wider 9 pixel source aperture.}\label{fig:starPostageCenAp9px}
\end{centering}
\end{figure}

When using a wider aperture (9 pixels), the photometric stability is much improved and the 0.5\% transit depth is readily visible in Figure \ref{fig:refCorrectedPhotJun12}.
The Kepler-based ephemeris indicates a transit at JD = 2457551.830.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/refcor_01.pdf}
\caption{Reference-corrected photometry for \shStar\ near the transit at JD = 2457551.830 (UT 2016-06-12).}\label{fig:refCorrectedPhotJun12}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/refcor_aug14.pdf}
\caption{Reference-corrected photometry for \shStar\ on UT 2016-06-14.}\label{fig:refCorrectedPhotJun14}
\end{centering}
\end{figure}

I experimented with a whole new set of reference stars (shown in Figure \ref{fig:newRefStars}) to see if they would work better for the time series on UT 2016-06-14.
I ended up with a very similar time series, as see in Figure \ref{fig:refCorrectedPhotJun14newStars}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/ut2016_04_14_analysis/st_labels}
\caption{A new set of reference stars that matched the source better in terms of brightness.}\label{fig:newRefStars}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/ut2016_04_14_analysis/refcor_01}
\caption{Reference-corrected photometry for \shStar\ on UT 2016-06-14, using a new set of reference stars shown in Figure \ref{fig:newRefStars}.}\label{fig:refCorrectedPhotJun14newStars}
\end{centering}
\end{figure}

The time series from UT2016-07-14 showed a sharp drop in flux for all stars as seen in Figure \ref{fig:ut2016-07-14clouds}.
Turns out is clouds, as visible in Figure \ref{fig:ut2016-07-14cloudImg}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/ut2016_07_14_tser_allstars.pdf}
\caption{All stars' photometry for \shStar\ on UT 2016-07-14.
There is a sharp drop in flux at 32.88 due to clouds}\label{fig:ut2016-07-14clouds}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_152.pdf}
\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_162.pdf}
\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_166.pdf}
\caption{Three example images during a cloud passage.}\label{fig:ut2016-07-14cloudImg}
\end{centering}
\end{figure}

>>>>

For the photometric reduction, we used the \texttt{ccdproc} package to generate master flat field and bias files.
I combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_152.pdf}
\includegraphics[width=0.5\textwidth]{images/stamps_kic1255_UT2016_07_14.pdf}
\caption{Target (src) and reference stars (numbered) used on UT 2016-07-14.
The reference stars were chosen to have similar count levels as the source. 
}\label{fig:ut2016-07-14cloudImg}
\end{centering}
\end{figure}
